Logsums

### 2020-05-11 04_accessibility.Rmd
Calculate 10-minute walk accessibility

>>>>

## 10-minute walk buffer

We are also interested in looking at what happens when the tracts are within a 
10-minute walk of a park, the threshold established by the Trust for Public Lands.

```{r nyc10mw}
access_10mw <- st_read("data/nyc_10mw.geojson") %>%
  st_cast("MULTIPOLYGON") %>%
  lwgeom::st_make_valid() %>%
  summarise(d = 1)

read_csv("data/tract_centroids.csv", col_types = "cnnnn") %>%
  st_as_sf(coords = c("LONGITUDE", "LATITUDE"), crs = 4326) %>%
  mutate(walk10 = st_intersects(., access_10mw, sparse = FALSE)) %>%
  st_set_geometry(NULL) %>%
  dplyr::select(geoid, walk10) %>%
  write_rds("data/walk10.rds")
```
